Transforming Trash as an Artistic Act

### 2016-01-08 chapter4_reduced.tex
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d

% başka bir yerde kullanırsın: , as illustrated by the examples cited so far,

@@

% The chapter that follows is divided into three sections

@@

%
%
% TODO: Be careful on tenses.
\section{The Statement}
% --disgusting, abject, unattractive, harmful to the people and nature--
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless and disgusting. Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.

% people are invited in the phase of collecting and finding trash that is every where and produced every time.
With the collaboration of many people discarded papers and packages were collected from different places. This time, it was not thrown away, it was collected and saved. Later they were transformed to notebooks by hand with traditional methods. Juxtaposition of trashes create notebooks that are different from the blank industrial ones, and through them challenged the widespread understanding of trash.

Through this project trash were re-imagined (re-considered, re-thought), new possibilities and alternatives were seek. As it is discarded, missed potentials were discovered.

The purpose is not to build an object that is produced from discarded material to watch it from distance. The important thing is to interact with it. It is already discarded and general behavior avoid from it. This work must change it. It must call the viewer to interact with it. Trash must be accepted by them. For this reason notebooks are given away free at various places where people visit frequently. By doing that once thrown materials would find a place with new purposes in the community.

% This project aims to find new potentials on trash. This project asks people to readmit the trash to the their life.

@@

% Starting from the very beginning, I would like to explain which paths and turns I took and how they let my work to come out as it is now. In other words, this will be the story of how I developed my work from scratch.

% Artist's work and their approach supported my project.
Through the process, there are several problems that needed to be solved. Some of the questions in my mind are solved through the research on trash. Further, the found samples of artworks helped me a lot to shape unclear points of the project. They provide me a deeper understanding of the subject and what I am doing. They lead me during the development of the work.
% played significant role, solved problems.
% It is evolved in time and affected from other artists' work, and gain meaning from research.

@@

% NEW PART [approach, history] 
Before explaining the details of the work, it would be better to explain how it was started and what is my approach to the trash. % It is not developed from scratch.

My interaction with discarded material is not limited with this thesis project. There are some previous attempts and several memories that I remember. Briefly, I want to examine them. These will also reveal my approach shaped through time (and how thesis work affected from it?). My motivation also revealed through it.

% [SODA CAPS]
I remember from my childhood that we were collecting soda caps and played with them. We were looking everywhere to collect them. Some caps were found less and they worth more in the game. We put them on the railways to make them flat. After the train had passed we had perfect flat caps for our games. At that time, it was not waste for us. It has a value and part of our games and indispensable source of fun. The notion of playing with it can be related with the Picasso's collage work \quotes{Still Life with Chair Caning} mentioned previously. He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials. We were already playing with trash while we were child. Therefore, it can be better understand that while Picasso said that \quotes{every child is an artist}.

@@

% [Song Dong]
The main idea is to save them to use later. For some people it is a life saving practice. It can be seen in the case of artist Song Dong's mother (mentioned in chapter 2). This practice result in establishing stronger (intimate) relationship with objects.

% TODO artist name

%Seeing papers on the waste bin is a disappointment for me. As stated by the artist Aaron Kramer \quotes{Trash is the failure of imagination} \cite{meyer2007turning}.

I am very uncomfortable with the act of discarding. I often think that by discarding objects, I am missing their potentials. I must find another use which is more effective than throwing away. At least I can give them to someone else who can use it for own purposes. As artist X argues that it is a "failure of imagination". There is a lot of effort to produce objects and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception. On the contrary, sometimes I became overwhelmed because of the significant amount of leftover from daily activities and in order to move on I need to leave them behind. It is the result of inevitable rhythm of modern life style. Consuming and wasting is part of people's daily routine and most of the time they are not aware of what they consume, and what they discard. In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines. The use of that object can be decided in the future.

% [encouraging point]
One of the encouraging factor of working on trash is to explore something different that others cannot see. In other words, it contains eureka moments. Because it is ignored by discarding and therefore undiscovered. Wait us to be discovered and possibly (as Picasso explanation on his work 'Bull's Head') discovered again and again.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
    \end{subfigure}
    \caption{Examples of early works}
    \label{fig:EarlyWorks}
\end{figure}

@@

% But covering things are not new actually, when we were studying at primary school, we covered our books and notebooks. My mother, she is also a teacher, still covers her books things whatever at hand. (I have remembered that we are covering our notebooks at school. Sometimes we also cover the books.)

% TODO referans hatası olabilir.
% NEW PART [collecting] 
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that 
\begin{quote}
Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \singlequotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
\end{quote}
I applied these instructions to my case and I checked some points regularly and seek the reason of why was it discarded. Details will be given later for each objects.

% There are similar points with my practice. I also check the condition of material.

% TODO Sanatçı adını bulmak gerekli.
% It can be viewed as mode of search for objects and it can be seen clearly on Dick Jewlss found photos.

% Firstly I need to explore different locations to collect items. Most of them are not obvious for me. I discovered them on the flow of normal life and tasks.

% The reason of why they are leaved behind is not obvious but technical errors, printing wrong versions and extra copies can be easily guessed after a little observation. Nobody cares others print out.

% The need to the item is ended up and it is least profitable to save it. Now it is considered as excess.

% Does it discarded because of rotten, not fitting industrial standard or being surplus (production excess)? For instance, in the documentary film of Agnés Varda, she records the potatoes that are discarded because of not fitting the industrial standards. Therefore these potatoes fall into the category of edible (eatable). They are in good quality but not liked shape???

% [Mode of search] looking for waste bins. asking for people. realizing during the daily life. for example bank splits. I discover them during my life. For instance,  after I leaved bank split I realized that I can use them in my notebooks. Back of the splits are empty and appropriate for writing. Lots of them are used in the bank. The other places are discovered while daily life continues.

@@

% OWNER
\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}. This question makes me feel uncomfortable because of thinking that stealing that someone elses' objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory. You already know that it owned by somebody else and after a while owner can take them. I solved this issue checking the leaved papers in every couples hours. If it stays there I take them. Further I encountered that If nobody takes them for a long time servants collect them.

% TODO reference gerekli.
% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
The issue of owner becomes more complicated when owners' social status considered. Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood. On the contrary when the same student went to Beverly Hills home of the many actors and celebrities in California to scavenge nearly the police were called.

% CONTRIBUTIONS OF PEOPLE
% Bu kısmın daha güzel anlatılması gerekli.
% TODO ref.
As mentioned previously many people contributed to the project by collecting. Whenever i meet my friends I ask them to save their discard. The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

@@

% They provide me the materials to transform it. They select the items and find them. They bring their approach and selection. They are part of the selection of the materials. They started to engage with the work. People bring the material also wonder the result of it. Further people see me when collecting objects and transporting them wonders their purpose.

% taxi drivers is wonder what will happen? they can not understand the idea here. not only collectors wonder but also people see me in action wonder the reason of it.

@@

% TODO What type of activities generates waste.
% Beyond social status it reveals activities that generate such a waste.
It can be also extracted that most of the trashed papers are thrown away from feeding activity. On the other hand vastness of some types of disposables reveal the dark side of the some enterprises such as Starbucks and Burger King. Few people thought that after seeing the project I only collected Starbucks packets. There is no such a limitation but as a result of habitat the number of them suppress the others.

@@

% [Production, Recycling] \paraphrase{All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes. Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper. Recycling paper can greatly diminish demand for virgin fiber from wood. However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely. It can only be recycled four to six times, as the fibers get shorter and weaker each time. In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.}

@@

% [importance of paper for me]
% ilki resimden geliyor. Onu toplamaya başladım. ve daha onu tükettiğimi düşünmüyorum. bana hala bir sürü imkan tanıdığını düşünüyorum. Bir de yaygın kullanılması. Hala daha kimsenin görmediği küçük noktaları görmeye başlamamış olabilir.

% The importance of paper cames from previoulsy I mentioned.

% Not only important for the community but also for me.

% Kagit benim cevremde cok fazla kullanilan bir sey. yaygın kullanımı olması.

@@

Collected items are stored in my room for a long time. Most of them are not belong to me. Here the detailed information of the collected materials including the place where it is collected and their usage are listed.

% Bu resme gerek olmayabilir. Appendixe konulabilir.
\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
  \caption{Collected materials}
  \label{fig:CollectedAllTogether}
\end{figure}

% Packets and Bags.

% Bir kısmı çalıştığım ofiste tüketilen kahve paketlerinin ve onların taşındıkları poşetlerden oluşmakta. Diğerleri arkadaşın ofisinden, bir kısmı ise hocamdan. Bir kısmı da benim yoldan topladıklarım.

% Toplama mekanları: Yollar, Bilkent labı. Sabahleyin geçtiğim yollarda genelde öğrencilerin bıraktıları simit pohaça gibi şeylerin paketleri bulunmakta.

% Toplanan malzemeler ve toplanan mekanlar. Bilkent labaratuvarı, Restraurants, Pazar yeri, Kendi çalıştığım ofis,

% Toplanan eşyalar mass produce üretilmiş ürünlerden oluşmakta.

% Toplanan eşyalar çok fazla özel eşyalardan oluşan şeyler değil. Evsel atık değil. Evin dışından toplanan şeyler değil. Daha çok halka açık alanlarda üretilen çöpler benimki. Yani Tracey eminin kiler gibi benimkiler kişisel eşyalardan oluşmamakta.

% Bu yüzden aslında toplanan eşyalarda kullanıcılarına ait çok fazla bir şey yok. Labdan alınanlardan olmakla birlikte, paket ve poşetlerde böyle bir durum yok. Found photosdaki gibi bir ilişki de yok mesela.

% Elimde bazılarının fotoğrafları var bazılarının ise yok. Yani bazılarının kayıtları var, bazılarının ise yok.

% Detaylı olarak bakmak gerekirse;

\textbf{Burger King packages} are collected from the office where I work. At launch time, some of the colleagues order the meal from Burger King which is a global chain of hamburger fast food restaurants. Meals are delivered to the office with paper packages. The package of the meal is collected and used as a cover of notebooks.

% Yemek posetleri. Ogle vaktinde kurye tarafindan teslim ediliyor. Kağıt, yağı iyi emdiği için kullanılıyor burada.

% Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy. Some people think that it is disgusting because of greasy onto it. But immediately I replied them just not you eat that greasy fires so what is wrong with it. At that time what Susan Strassed said comes my mind. (it fits here)

% Nothing is inherently trash(5). matter out of place. Dirt is relative emphasize. "Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on" (Douglas 2003, 36-7)

Why people throw them away varies. Through my experience I can give one anecdote that I encounter frequently. When I collect the papers under the dishes or food packages, people often think that it is disgusting and called them as dirty. However, it is very strange that the fat on the paper was previously what they are eating.

\textbf{Starbucks packages} are collected from my supervisor, office and my friend. Especially my supervisor and friend saved and collected them from their friends. They are used as a cover of notebooks. There are different types of packets from this category. for some of them are build from recycled (precisely downcycled) paper, and the others packages for coffee beans. they are airtight and waterproof packages very solid and strong. and well graphic design with different color and illustration.

\textbf{Modshifters papers} that are covered on table and at the end of the day they are cut out and throw away. I go this place many times and every time questioned what they are doing to the papers. One of my visit we stay there at a late time and catch the garson collecting the old papers and preparing tables to the next customer or day. I ask him to give me and he kindly accepted. From this paper I covered [x] notebooks. All of them contains track of people who sit down there. I do not know them and I am not sure that the paper that they are sit down turned to such a thing.

% Masaların üzerine örtülen ve sonra atılan kağıtlar.

% Bir yandan da kağıtların nasıl kullanıldıklarına dair bir gösterge. Yemek için kullanılıyor. Gıda sektörü için.

% Buradaki kağıtlar tüm yemek masasının üzerine örtüyor. büyük bir rulo halinde masanın başında bulunuyor. yemek yendikten sonra masanın üzerindeki kısım yırtılıp atılıyor. yenisi rulodan seriliyor. ne kadar kağıt harcandığı bir bakışta anlaşılmakta. Tüm o rulodaki kağıtlar çöpe gidecek. Arkadaşlarla bir gün dışarı gittikten sonra buradaki kağıtları farkettim ve çıkışta onlar eskileri toplarken kağıtları topladım.

\textbf{Varuna Gezgin}, is a cafe. papers of old menus. They are waited to be discarded.

% arkadaşlarla yemeğe gittikten sonra kasiyerdeki arkaştan defterleri burada verip veremeyeceğimi sorduktan sonra bana ellerindeki kağıtlardan bahsetti ve onları verebileceğinden bahsetti.

% amacim aslinda sadece yemeklerin altindaki kagitlari toladiktan sonra bunlari bunrada gosterebilir miyiz diye sormakti. Ama sonrasinda konusmamizda bana bir suru kagit getirdi. Ellerindeki kullanilmayan kagitlarin sadec bir kismiydi. Zatenben tek basima cok ufak kucuk bir kismina dokumus oluyordum bunkaron. Hatta kasadaki cocuk kalanlari da ogrencilere dagitmayi dusundu. En azindan kenarda bekleyen kagitlar gun yuzue cikmis oldu.

% burdaki dikkate alinan sey satilan bir sey olmadigdi. Ktuphanede ise aslinda bunun bir reklam anlami tasiyip tasimayagi idi. Bilkent labindakiler ise bunukomsenin almayacagi dokunmayacagi yonundeydi. E napalim artik. Insanlarla konustukca farkli seyler dusunuyorum.

% websitesinde amac bunlari anlatabilmekti.

\textbf{Graduation banner} Because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011). Every piece was a part of bigger banner. At that time there are serious debates about freedom on the internet. Most of the website are banned from the decision to the courts and they were not accessible. (Access to this banner is blocked by a court decision.) In Middle East Technical University there is a tradition that in graduation ceremony people walk through in the stadium and greet to the tribunes. With this event they carry some banners to express their feelings and criticize some realities in the country. This one of them. It is carried by students (new grads of Computer Engineering) The slogan decided by among the students and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes. After the ceremony I could not throw away this banner. I do not know what to do it, it is very big actually to store but I could not. I think that I will figure out later. Maybe I can use it as a draft paper. But is it worth to cut out this all long banner etc. Also to strengthen the banner and to prevent to tear while carried by the many people we are tape it from its boundaries. In other words some of the areas can not appropriate for writing. When I decided to this topic I remembered to this banner. It is stands in a corner in a dusty way. Now it is time use it. It waited very log time and it is time to revive again. Currently In turkey the problem of banning web-sites continues. Event it can said that people do not surprises when a website is blocked by the courts. It can be turn be a paper that people can freely express their ideas and feeling onto the it. Cut out them to the smaller pieces and make them as notebooks. They are part of puzzle. for the smaller parts what is written on them can not easily understandable. To realize what is the message is you have to bring together all of them again. But It is not possible, therefore website is a very good solution for them. All pages have unique patterns. Remaining parts of letter and tape. It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
  \caption{Banner}
  \label{fig:Banner_1}
\end{figure}

\textbf{Tea bags} are collected from my friend. Their a couple of consumption of tea and their covers.

% Gıda sektörüne bir diğer örnek.

\textbf{Order slips} are collected from bank office my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
% [Everywhere, everytime, Life practice.] En başta bahsettiğim everywhere, everytime aslında collecting ile çok yakından ilgili. Bu toplama işlemi normal hayatın içine sızıyor(infiltrate the life). iş bankası örneğinde anlatılabilir. bir de art gallery found object örneği verilebilir.

\textbf{Elginden gelen kağıtlar}

%arkadastan gelen kagitlar.

% Ders için kullanılanlar. Arkadaştan gelen kağıtlar, ders notları, tez yaprakları.

\textbf{Bilkent kağıtları} % bu kısım found photos ile ilişkilendirilebilir.

>>>>

@@

@@

%
%
% TODO: Be careful on tenses.
\section{The Statement}
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless, disgusting, abject, unattractive, and harmful to the people and nature. Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.

With the collaboration of many people discarded papers and packages were collected from different places. This time, it was not thrown away, it was collected and saved. Later they were transformed to notebooks by hand with traditional methods. Juxtaposition of trashes create notebooks that are different from the blank industrial ones, and through them challenged the widespread understanding of trash.

Through this project trash were re-imagined (re-considered, re-thought), new possibilities and alternatives were seek. As it is discarded, missed potentials were discovered.  This project aims to find new potentials on trash.

The purpose is not to build an object that is produced from discarded material to watch it from distance. The important thing is to interact with it. It is already discarded and general behavior avoid from it. This work must change it. It must call the viewer to interact with it. Trash must be accepted by them. This project asks people to readmit the trash to the their life. For this reason notebooks are given away free at various places where people visit frequently. By doing that once thrown materials would find a place with new purposes in the community.

@@

Through the process, there are several problems that needed to be solved. Some of the questions in my mind are solved through the research on the subject. Further, the found samples of artworks played significant role in progress. They helped me a lot to shape unclear points of the project. They provide me a deeper understanding of the subject and what I am doing. In other words, they lead me during the development of the work.

@@

% NEW PART [approach, history] 
Before explaining the details of the work, it would be better to explain how it was started and what is my approach to the trash.

My interaction with discarded material is not limited with this thesis project. There are a few previous attempts and several memories that I remember. Briefly, I want to examine them. These will also reveal my motivation and approach shaped through time and how thesis work affected from it.

% [SODA CAPS]
I remember from my childhood that we were collecting soda caps and were playing with them. We were looking everywhere to collect them. Some caps were found less and they worth more in the game. We put them on the railways to make them flat. After the train had passed we had perfect flat caps for our games. At that time, it was not waste for us. It has a value and part of our games and indispensable source of fun. The notion of playing with it can be related with the Picasso's collage work \quotes{Still Life with Chair Caning} mentioned previously. He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials. We were already playing with trash while we were child. Therefore, it can be better understand that why Picasso said that \quotes{every child is an artist}.

@@

% [Song Dong]
The main idea is to save them to use later. For some people it is a life saving practice. It can be seen in the case of artist Song Dong's mother (mentioned in chapter 2). This practice result in establishing stronger and intimate relationship with objects.

I am very uncomfortable with the act of discarding. I often think that by discarding objects, I am missing their potentials. I must find another use which is more effective than throwing away. At least I can give them to someone else who can use it for own purposes. Seeing papers on the waste bin is a disappointment for me. As artist Aaron Kramer argues that \quotes{[t]rash is the failure of imagination} \citep[as cited in][]{meyer2007turning}. There is a lot of effort to produce objects and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception. On the contrary, sometimes I became overwhelmed because of the significant amount of leftover from daily activities and in order to move on I need to leave them behind. It is the result of inevitable rhythm of modern life style. Consuming and wasting is part of people's daily routine and most of the time they are not aware of what they consume, and what they discard. In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines. The use of that object can be decided in the future.

% [encouraging point]
One of the encouraging factor of working on trash is to explore something different that others cannot see. In other words, it contains eureka moments. Because it is ignored by discarding and therefore undiscovered. It waits us to be discovered and possibly (as Picasso's explanation on his work 'Bull's Head'\footnote{See epigraph in the beginning of Chapter 3}) discovered again and again.

@@

\begin{figure}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
    \end{subfigure}
    \caption{Examples of early works}
    \label{fig:EarlyWorks}
\end{figure}

@@

% TODO Lars Eighner BIB'e eklenecek.

% NEW PART [collecting] 
\subsection{Collecting}
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that

\begin{quote}
Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \singlequotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
\end{quote}

Does it discarded because of rotten, not fitting industrial standard or being production excess? For instance, in the documentary film of Agnés Varda, she records the potatoes that are discarded because of not fitting the industrial standards. Therefore these potatoes fall into the category of eatable.

I applied above instructions to my case and I checked discovered places regularly and seek the reason of why was it discarded. I also checked the condition of material. However I need to explore different locations to collect items. Most of them are not obvious for me. I discovered them on the flow of normal life and tasks. Similar to the methodology of Dick Jewell when searching for photos, my mode of search includes waste bins. However every object have a different story and they will be explained later.

@@

% OWNER
\quotes{The question of who owns these discards is not trivial} \citep{zimring2012encyclopedia}. This question makes me feel uncomfortable because of thinking that stealing that someone elses' objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory. You already know that it owned by somebody else and after a while owner can take them. I solved this issue checking the leaved papers in every couples hours. If it stays there I take them. Further I encountered that If nobody takes them for a long time servants collect them.

The issue of owner becomes more complicated when owners' social status considered. Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood \citep[as cited in][]{pricano2011trashtalk}. On the contrary when the same student went to Beverly Hills home of the many actors and celebrities in California to scavenge nearly the police were called.

% CONTRIBUTIONS OF PEOPLE
As mentioned previously many people contributed to the project by collecting. Whenever I meet my friends I ask them to save their discard for the project. The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

@@

They provide me the materials to transform it. They select the items and find them. They bring their approach and selection. They are part of the selection of the materials. They started to engage with the work. People bring the material also wonder the result of it. Further people see me when collecting objects and transporting them wonders their purpose.

@@

% What type of activities generates waste.
Beyond social status it reveals activities that generate such a waste.It can be also extracted that most of the trashed papers are thrown away from feeding activity. On the other hand vastness of some types of disposables reveal the dark side of the enterprises such as Starbucks and Burger King. Few people thought that after seeing the project I only collected Starbucks packets. There is no such a limitation but as a result of my habitat the number of them suppress the others.

@@

@@

The reason of collecting papers based on my interest on painting and writing. This medium offers me great possibilities that I cannot consume yet. This project is one of them.

% TODO see figure appendix.
Collected items are stored in my room for a long time. Most of them are not belong to me. Here the detailed information of the collected materials including the place where it is collected and their previous usage are listed.

\textbf{Burger King packages} are collected from the office where I work. At launch time, some of the colleagues order their meal from Burger King which is a global chain of fast food restaurant. Meals are delivered to the office with paper packages. The package of the meal is collected and used as a cover of notebooks.

Inside the bag one paper package is used for French fries which is oily and paper is very good to absorb oil. Some people think that it is disgusting to use it for other purposes because of oil onto it. But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time what \cite[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}. She refers to resolution on dirt of \cite[36]{douglas2003purity}:
\begin{quote}
Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on.
\end{quote}

This simply explains that our perceptions to the objects are relative and change in their usage context.

\textbf{Starbucks packages} are collected from my supervisor, office where I work and my friend. Particularly my friend saved and collected them from her friends. Few of them collected from waste bins. They are used as a cover of notebooks. There are different types of packets from this category. As claimed by the company all of them are build from recycled ---precisely downcycled--- paper. There is also one category of object that is not paper. It is package of coffee beans. It is airtight and waterproof. It is very solid and strong. It has well graphic designs with different color and illustration.

\textbf{Modshifters papers} are used to cover the dinner table. Beginning of the table there is a big roll of paper to cover the table. At the end of the day used parts are cut out and thrown away. One of my visit I stayed there at a late time and catch the waiter when collecting the used papers and preparing tables to the next customer. I asked kindly him to give me these papers and he accepted. They are used as a cover of notebooks. All of them contains track of people who sit down there. I do not know any of them and I am not sure that the paper that they are laid down on their dinner turned to such a thing.

\textbf{Varuna Gezgin papers} are the pages of obsolete dinner menu. When leaving there I showed my notebooks and asked to the cashier that I could able to present them at Varuna Gezgin. He immediately mentioned their vast amount of unused papers and gave me some of them that I can able to carry with me. This was a very strange experience for me because I did not expect such a thing. These paper are used inside of the notebooks as a page.

\textbf{The banner} is carried at graduation ceremony of Middle East Technical University in 2011 by the new Computer Engineering graduates. In Middle East Technical University there is a tradition that in graduation ceremony new grads walk through in the stadium and greet to the tribunes. With this event they carry some banners to express their feelings and point out the issues of the country in an ironic and humorous way. This one of them. At that time there are serious debates about freedom on the web. Most of the website are banned from the decision to the courts and they were not accessible. The slogan (Access to this banner is blocked by a court decision) decided by the new grads and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes.After the ceremony I could not throw away this banner. I do not know what to do it. It is a very big roll of paper to save but I could not throw away. I think that I will figure out later. Maybe I can use it as a draft paper. However is it worth to cut out this all long banner? Moreover to strengthen the banner we tape it from its boundaries. In other words some of the areas can not appropriate for writing. When I decided to my thesis subject I remembered to this banner. It stands in a corner in a dusty way. Now it is time to use it. It waited very log time and it is time to revive. I cut out them to the smaller pieces to use them as pages of notebooks. All pages have unique patterns. They contain parts of letters. Most of the time it is not recognizable belongs to which letter. These papers offers unique writing experience to the writer because of the patterns of letters and residue of tapes.

By the way currently in Turkey the problem of banning web-sites continues. Event it can said that people do not surprises when a website is blocked by the courts. In other words still the slogan preserves its significance and through this project people will remember these days.

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
  \caption{The banner carried by new grads, 2011}
  \label{fig:Banner_1}
\end{figure}

\textbf{Order slips} are collected from bank office located at Technopolis of Middle East Technical University. They are used to record the order of customers. I realized that back of them are empty and appropriate for writing. Further there many others are waiting on the bin. After this experiment I really convinced that I am really looking for trash everywhere every time. The act of collecting spread through the every moment of life.

\textbf{A4 photocopy papers} are collected from Bilkent Computer Laboratory. In every lab there is a one printer. However when someone wants to print computers suggest firstly printer on the room 307. This result in many confusions and extra prints. I explored this place during my thesis research. I went there to print out draft of my thesis. I encountered that many papers are leaved on the tables.  The reason of why they are leaved behind is not obvious but technical errors, printing wrong versions and extra copies can be easily guessed after a little observation. Nobody cares others print out. Papers are mostly composed of lecture notes. I collected many papers from there and they are used as a page of notebooks. I do not know owner of them and possibly users of notebooks so. However it will increase our realization of what other students in this university are dealing with.

Similar type of papers are also taken from my friend. They are composed of his lecture notes. He donated them to the project.

Collected items are not limited with these but for the others there are no special memory. Tea bags, collected packages from the streets are some of them.

Most of the materials that I collect are mass produced items. Generally their usage fall into the two category; education and food industry. They are found on public places. They are not personal objects like in the work of Tracey Emin's \quotes{My Bed} even if it can be claimed that the collected papers from the laboratory contains personal travel tickets. Identity of owner are not certain.

% Elimde bazılarının fotoğrafları (kayıtları) var bazılarının ise yok.

% burdaki dikkate alinan sey satilan bir sey olmadigdi. Kütuphanede ise aslinda bunun bir reklam anlami tasiyip tasimayagi idi. Bilkent labindakiler ise bunukomsenin almayacagi dokunmayacagi yonundeydi. E napalim artik. Insanlarla konustukca farkli seyler dusunuyorum.

% ozellikle resterantlardan bunkari tplarken, genekde garsonlar hemen almaya calisiyorlardi. Ben topladigimi soylerken bu zman yenisini getirmeyi teklif ediyorardi. Bu benim onceden bahsettigimaz tuketme kurali ile celismekteydi ve ben bunu reddediyordum.

% NEW PART [transforming]
\subsection{Transformation}
At one side while paper is being collected, on the other side I started to make experiments with the material. I questioned what else can be made with these collected materials and tried to cover (wrap out) objects and plants in the public. However these do not give the result what I want. People cannot interact with these and possibly they will turn to trash again. For that reason the first approach which is making notebooks are more appropriate to accomplish the purpose.

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
    \end{subfigure}
    \caption{Experiments with collected papers}
    \label{fig:ExperimentWithPaper}
\end{figure}

% [notebooks]
There are two main parts of notebooks; cover and pages. Papers that are mostly blank(empty) are used inside of the notebooks for writing. Others that are solid and colorful are used as a cover for notebooks. Mixing (juxtaposing) materials is main method in the production process. I combine different papers and packages. I try to generate every possible combination. The purpose is to create as many alternatives as I can because trash is ignored and people do not give it new alternatives. Therefore these notebooks provide many alternatives to show that otherwise is possible.

I followed the methods of Dada poem to mix the papers used inside of the notebooks. I changed their order and direction. 
\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem};

% TODO refre
\begin{quote}
Take a newspaper.\\
Take some scissors.\\
Choose from this paper an article the length you want to make your poem.\\
Cut out the article.\\
Next carefully cut out each of the words that make up this article and put them all in a bag.\\
Shake gently.\\
Next take out each cutting one after the other.\\
Copy conscientiously in the order in which they left the bag.\\
The poem will resemble you.\\
And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

% TODO muhakkak tekrar kontrol etmek gerekli.
Size of the paper used inside of the notebooks are mostly equals to the size of an A4 sheet. Usage of papers differs among the notebooks. Especially for the papers taken from Varuna Gezgin written part is folded inward by hiding it. However for the ones collected from Bilkent Computer Laboratory written side of it leaved open. Their content comes from various students whose departments are also various. In other words offers great diversity and they are mixed to allow different interpretations. Further it provides what students from other departments works on. What other students work on can be understand from these.

There are different dimensions of notebooks. Most of them are half of A4 or quarter of it.

% TODO defter dikme yönteminin fotoğrafı

The tools used in the making of notebooks are as follows; needle, sewing thread, scissors, utility knife, pushpin, silicone, caulking guns.

While transforming collected materials my method can be explained with the term upcycling mentioned at the end of the Chapter 1. Further I tried to use objects already at hand. In other words I followed the bricolage technique. However I have to do buy some tools for my work. Therefore it is hard to consider it as bricolage but my intention is to follow it.

% The purpose is here to increase the diversity.

@@
